Linking different metrics to Elaboration and Innovation

### 2023-05-16 Analysis/15-linking_metrics.Rmd
Create 15-linking_metrics.Rmd

par(mfrow = c(1,2))
plot(NULL, xlim = range(unlist(clade_disp)), ylim = range(unlist(clade_elab)), xlab = "Eigen dispersion", ylab = "Elaboration")
points(clade_disp$gulls, clade_elab$gulls, pch = 19, col = "darkgreen")
points(clade_disp$sandpipers, clade_elab$sandpipers, pch = 19, col = "blue")
points(clade_disp$plovers, clade_elab$plovers, pch = 19, col = "orange")
legend("topright", pch = 19, col = c("darkgreen", "blue", "orange"), legend = c("gulls", "sandpipers", "plovers"))

plot(NULL, xlim = range(unlist(clade_disp)), ylim = range(unlist(clade_inov)), xlab = "Eigen dispersion", ylab = "Innovation")
points(clade_disp$gulls, clade_inov$gulls, pch = 19, col = "darkgreen")
points(clade_disp$sandpipers, clade_inov$sandpipers, pch = 19, col = "blue")
points(clade_disp$plovers, clade_inov$plovers, pch = 19, col = "orange")
```

@@

par(mfrow = c(1,2))
plot(NULL, xlim = range(unlist(species_resp)), ylim = range(unlist(species_elab)), xlab = "Respondability", ylab = "Elaboration (evolvability)")
points(species_resp$plovers, species_elab$plovers, pch = 19, col = "orange", cex = 0.5)
points(species_resp$sandpipers, species_elab$sandpipers, pch = 19, col = "blue", cex = 0.5)
points(species_resp$gulls, species_elab$gulls, pch = 19, col = "darkgreen", cex = 0.5)
legend("topright", pch = 19, col = c("darkgreen", "blue", "orange"), legend = c("gulls", "sandpipers", "plovers"))

plot(NULL, xlim = range(unlist(species_resp)), ylim = range(unlist(species_inov)), xlab = "Respondability", ylab = "Innovation")
points(species_resp$plovers, species_inov$plovers, pch = 19, col = "orange", cex = 0.5)
points(species_resp$sandpipers, species_inov$sandpipers, pch = 19, col = "blue", cex = 0.5)
points(species_resp$gulls, species_inov$gulls, pch = 19, col = "darkgreen", cex = 0.5)
```

 - [ ] link orthogonality to random skewers
 - [x] link E/I to relative eigenvector dispersion (Pavlicev et al., 2009, Watanabe, 2022) 
 - [x] link E/I to conditional evolvability (Hansen & Houle, 2008) 
 - [ ] link E/I to integration (Hansen & Houle, 2008)

>>>>

pdf("../Manuscript/Figures/elaboration_innovation_dispersion.pdf", width = 12, height = 6)
par(mfrow = c(1,2))
plot(NULL, xlim = range(unlist(clade_disp)), ylim = range(unlist(clade_elab)), xlab = "Eigen dispersion", ylab = "Elaboration")
points(clade_disp$gulls, clade_elab$gulls, pch = 19, col = "darkgreen")
points(clade_disp$sandpipers, clade_elab$sandpipers, pch = 19, col = "blue")
points(clade_disp$plovers, clade_elab$plovers, pch = 19, col = "orange")
legend("topright", pch = 19, col = c("darkgreen", "blue", "orange"), legend = c("gulls", "sandpipers", "plovers"))

plot(NULL, xlim = range(unlist(clade_disp)), ylim = range(unlist(clade_inov)), xlab = "Eigen dispersion", ylab = "Innovation")
points(clade_disp$gulls, clade_inov$gulls, pch = 19, col = "darkgreen")
points(clade_disp$sandpipers, clade_inov$sandpipers, pch = 19, col = "blue")
points(clade_disp$plovers, clade_inov$plovers, pch = 19, col = "orange")
dev.off()
```

@@

pdf("../Manuscript/Figures/respondability.pdf", width = 12, height = 6)
par(mfrow = c(1,2))
plot(NULL, xlim = range(unlist(species_resp)), ylim = range(unlist(species_elab)), xlab = "Respondability", ylab = "Elaboration (evolvability)")
points(species_resp$plovers, species_elab$plovers, pch = 19, col = "orange", cex = 0.5)
points(species_resp$sandpipers, species_elab$sandpipers, pch = 19, col = "blue", cex = 0.5)
points(species_resp$gulls, species_elab$gulls, pch = 19, col = "darkgreen", cex = 0.5)
legend("topleft", pch = 19, col = c("darkgreen", "blue", "orange"), legend = c("gulls", "sandpipers", "plovers"))

plot(NULL, xlim = range(unlist(species_resp)), ylim = range(unlist(species_inov)), xlab = "Respondability", ylab = "Innovation")
points(species_resp$plovers, species_inov$plovers, pch = 19, col = "orange", cex = 0.5)
points(species_resp$sandpipers, species_inov$sandpipers, pch = 19, col = "blue", cex = 0.5)
points(species_resp$gulls, species_inov$gulls, pch = 19, col = "darkgreen", cex = 0.5)
dev.off()
```
